Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2014-11-21 figure_table.tex
SI papers reading

antidazzle window, electrochemical intercalation, coloration-bleaching kinetics, present as a minor phase, 
(i.e. )
(cf. )
up-scaling capability, band edge smeared; major bands situated at

>>>>

antidazzle window, electrochemical intercalation, coloration-bleaching kinetics, present as a minor phase, 
(i.e. )
(cf. )

put under the spotlight, barely satisfactory, decrement of,  more numerous than elsewhere, draw attention to it. not as restrictive an assumption as it may seem.

up-scaling capability, band edge smeared; major bands situated at, 
bypassing a limitation, held back by a restriction, discern,  nanoscopy, run in parallel tracks, line of thought take shape, delve into, devise, commotion, fruition, foundation was laid, one variant, ponder, passivated, halt, lack of progress, p-dope FaN in a controlled manner, transcend, theoretical description, and experimental implementation,

stochastic, doctrine, ample evidence, suits - diamonds, clubs, hearts, and spades

settling towards minimum energy, a free electron of momentum $p$ cab be represented by a wave of wavelength $\lambda = h/p$. to the extent to which theoretical results correspond with reality. apparent agreement of theory and experiment carries no guarantee that . another school of thought,

bottom-up paradigm. curiosity was drawn toward. exemplify. unambiguous interpretation. pronounced, Nevertheless, highlight the necessity , As a consequence, proved beneficial. insight we have gained from our investigations. solve this conflict. critical ingredients. regime. dominate and reveal itself.

closer inspection, consecutive, a characteristic feature of aggregation process. on the basis of present results, some conclusion could be drawn concerning the .. The observation that .... indicated .... ,discerned, discrepancy, deviating, deviation, accompanied,

progressively consumed and converted into sulfide. ensuing purification, a matter of controversy,

entail, prerequisite, kinetically hindered, rate-determining step, confirmed experimentally. closed cap. various synthetic methodologies.
grouping into two categories, phenomenological arguments, primarily, establish a systematic connection. 
in this letter, reason reside in, sizing histogram, vessel, implementation of , predominantly, stacking sequence.
naturally abundant, fundamentally intriguing and technologically attractive, thermodynamically preferred. 
pronounced effect, strategy for extending methodology, modify, change, alter.

exothermic, endothermic. occurrence, impediment, batches. prevail in accordance with

measured properties compare favorably with theoretical analysis. 
elimination of dangling bonds. conformal coating. Equation is visualized in Fig.
fluidic dynamics, entangled web, dimensional heterostructure, kinetically hindered. preceding text, more specifically, hold great potential. 
residence time, crucial aspects. temperature gradient. diverse function, distinct experiment.

trigonal prismatic coordination, bridging coordination types. intercalation mechanism been elucidated 
hydration. not always deleterious, branched nanocrystal, orientation dictated by substrates, moscovite mica, concurrently, as described herein. applicable, suggestive, anion-terminated facets. phase segregation.

Inorganic fullerenes, transitional metal dichalcogenides. postulate

vast, disorder, orderliness, irregularly, solidifies, 
a constant competition between the attractive force which hole the atoms together and the irregular motions which tend to knock them apart. 
Liquid and gas are alike in their ability to flow but unlike in the volumes they occupy, while liquid and solid are alike in the volumes they occupy but unlike in their ability to flow.

the departure of molecules from most solids at ordinary temperature is so infrequent that the evaporation is imperceptible. 
one kind of disorder and limitless orderliness. endless variety, diversity, ingredient, grows into being. They adopt positions on the surface that are forced on them by the kind of orderliness confronting them. Settling into those positions, they extend the orderliness outward, and thus the crystal grows.

manifest their presence in various ways. impartially, small proportion, interstitial vacancy, point, line, plane disorder. the few layers of atoms near the surface will be slightly more compressed  inward than the bulk of the crystal. entangle, agitate, the increasing viscosity of liquids as their temperature goes down is a measure of the increasing difficulty with which the molecules move past one another.

more distant past, rock, mineral, percolate, steam boiler, 
Snow flakes grow directly from moist air-in other words, from a gas. Carbon dioxide fizzes out of soft drinks when you release the pressure. dissolved or mixed, 
Gases are usually less soluble in a liquid when it is hot than when it is cold, but the reverse is usually true of solids. The opposite effects arise from the same cause: increasing temperature tend to increase their disorder.

True solution: they are dispersed through one another molecularly, not in little chunks. 
The solubility of the substituent is limited, much as is the solubility of salt in water. retain the crystalline arrangement.

Zinc and copper, silver and gold. 
When molecules of solute are moving about in a liquid, they cannot go as far in as short a time as they can when they are moving about in a gas: the diffusion rate is much slower. Perfume in air,

Soldering depends on dissolving a little of the solid metal in the molten solder to form an alloy at the boundary;

Factors that influence whether a substance will dissolve in something else: the random motion of the molecules, tending to separate and disorder them, wage a constant war with the attractive forces.

The associations between the molecules of solute and of solvent keep forming and breaking and forming again.

water reduces the electric forces more than almost any other liquid does, a reason why water is an effective solvent for materials whose molecular constituents bear electric charges.  A bare ion attracts a few water molecules, behaving like a new charged compound. It is this charged molecule, not the bare ion, which moves around through the solution. (hydration of an ion)

Attached water, watery clothing.

### 2014-11-21 misc/SI_thesis.tex
camera ready
SI papers reading

\chapter{wo3}
metal oxide contact on work function and band structure.\cite{Greiner2013}

@@

\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Name & Raman Shift (\si{cm^{-1}}) &  Ref   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na2W4O13} & &\\
\ce{Na5W14O44} & & this work\\
\bottomrule
\end{tabular}
Materials in solid state, 
vw-very weak; w-weak; m-medium; s-strong; vs-very strong
\end{table}

@@

@@

>>>>

\chapter{wo3}

\ce{WO3} crystalline film ECD, electrochemical anodized, \cite{Ou2012}

metal oxide contact on work function and band structure.\cite{Greiner2013}

@@

\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten compounds}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Phase & Raman Shift (\si{cm^{-1}}) &  Reference   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na2W4O13} & 949(m), 794(s), 777(vs), 366(w), 311(w), 272(w), 263(w) &\cite{Fomichev1992}\\
\ce{Na5W14O44} & 965(m), 943(m), 913(w), 765(vs), 695(m), 107(s) & this work\\
\bottomrule
\end{tabular}
Materials in solid state, 
vw-very weak; w-weak; m-medium; s-strong; vs-very strong
\end{table}

@@

\section{heterojunction}

arix1410.8201: contact resistance at TMDC/metal interface due to Schottky barrier. \ce{MoS2} transistor is a Schottky barrier transistor with effective barrier height controlled by gate and drain biases. The carrier path for n-type \ce{MoS2} defined from source to drain. Thermal-assisted tunneling from source metal Fermi level to the channel. To reduce the contact resistance in \ce{MoS2} FET, 
\begin{itemize}
\item low $\phi$ contact metal
\item heterojunction with graphene 
\item heavily doping the source/drain region
\item substitute doping of \ce{Cl-} for \ce{S2-}, $\sigma = $
\end{itemize}

Fermi-level pinning at semi interface due to sulfur vacancies.\cite{Liu2013c}

\ce{MoO_{3-x}} as high workfunctio material aligned deeply into the VB of \ce{MoS2} as a p-contact,\cite{Battaglia2014} \cite{Chuang2014a} \ce{MoO_{3-x}} forms defect states within the band gap,

PEI as n-type surface dopant,

electron density in \ce{WS2} to be 6E11 \si{cm^{-2}} ref95,\cite{SikHwang2012}

scanning tunneling spectroscopy. \ce{WSe2} with Fermi level at 1.15 eV below conduction band. \cite{McDonnell2014} The use of binding energy shift in the core level as a measure of band bending at interfaces. \ce{MoS2} exhibit both p-type and n-type behavior due to local variation in stoichiometry. 0.3\% areal density was found to be able to dominate the electron Schottky barrier height.

\ce{MoS2}, photoionization energy $5.47\pm0.15$ eV, \cite{Schlaf1999}, and  bandgap of 1.17 eV, deriving the electron affinity as $\chi_A= 4.3\pm0.15$ eV.

interface dipole \cite{Lin2013a}
MX2 electrolyte photocurrent measurement, \ce{MoS2} gap 1.17 eV, \cite{Kautek1980}

The electron affinity rule, band offset of \ce{SnS2} on \ce{MoS2}, linear models, comparison of model with experimental results difficult due to the uncertainties or superposition of physical effects.\cite{Schlaf1999} interdiffusion, chemical reaction across the interface. X-ray photoemission spectroscopy and ultraviolet photoelectron spectroscopy, valence band offset from XPS and UPS measurements; conduction bands are not accessible since photoelectron spectroscopy (PES) only allows the measurement of occupied DOS.
and $\Delta C$ is calculated using $\Delta V$ and $E_g$.

Some conventions used as following:
\begin{enumerate} 
\item Fermi level is zero energy;
\item binding energies are positive;
\end{enumerate}

\begin{table}[htb]
\centering
\caption{WS2 and  \ce{WO3}}\label{tab:woram}
\begin{tabular}{lccccr}
\toprule
Name & Nc & Nv &  $E_g$ (eV)   & $\chi$ & $\epsilon_{st}$  \\
\midrule
\ce{WO3} &    &     &  2.7    &      & 50\\    
\ce{WS2} &    &     &  1.9~1.5   &      & \\    
\bottomrule
\end{tabular}
\end{table}

\subsection{method}
angle-resolved photo-emission/photo-electron spectroscopy. (ARPES)
\[
E_binding = \hbar\omega - E_k - \phi
\]
where $E_k$ is kinetic energy of outgoing electron, which can be measured. $\phi$ is electron work function towards vacuum. $\hbar\omega$ is incident photon energy, and is varied. The UV-PS spectra represent the DOS integrated over all wave vectors. Normal emission UPS,

hall effect,

photoelectrolysis quantum efficiency,

\subsection{parameters for wo3 and ws2}

Lithium tunsten bronze, e mobility decrease with T; the decreasing mobility with higher T could be taken to indicate the principal mechanism for scattering the conduction carriers is by thermal motion of atoms in host lattice.  \ce{MxWO3} derived from a host of \ce{WO3} lattice doped with alkali metal M. \cite{Sienko1961}

\ce{WO3} valence band about 4 eV wide. \cite{Bringans1981}, \cite{DeAngelis1977}

semiconductor-electrolyte interface, parallel capacitance C, flat band potential, Schottky-Mott plot,\cite{DiQuarto1981} 
\[
\frac{1}{C_p^2} = \frac{2}{\epsilon_0\epsilon e N_d} (U_E - U_{FB} - \frac{kT}{e})
\]
DOS $Neff$ as 1E20 \si{cm^{-3}eV^{-1}} and using 
\[
-qU_{FB} = E_F = E_{CB} + kT\log N_d/Neff
\]

quantum efficiency measurement of water photoelectrolysis. n-type oxide as anode, biased and forming a depleting region on the surface. $\alpha$ is proportional to $\eta$, and Tauc method was used to extrapolate band gap. \cite{Koffyberg1979}

12\% usage of solar spectrum, conductivity $\sigma = 6\times10^{-1}$ \si{\per\ohm\per\cm}, taking electron mobility as $\mu=10$ \si{cm^2\per Vs},\cite{Berak1970} the carrier density is 4E15 \si{cm^{-3}}.\cite{Butler1976} \ce{WO3} and SCE reference electrode in one cell, and Pt in the other. Pt cell was bubbled with Ar to remove dissolved \ce{O2}. pH changes shift the Fermi level of electrolyte; run a cell without applied potential is desirable, and \ce{WO3} is inferior to \ce{TiO2} in this respect. The bands are essentially flat, and depletion layer necessary for charge separation does not exist.

low energy photons sample mainly the valence electron structure of oxygen, and high-energy photons see the tungsten contribution more strongly.\cite{Bullett2000}

\begin{table}[htb]
\centering
\caption{band gaps of \ce{WO3}}\label{tab:wobg}
\begin{tabular}{cccc}
\toprule
Material state & energy gap (eV) & probing technique   & Reference   \\
\midrule
amorphous film & 2.62(i), 3.52(d)   &    photoelectrolysis  & $\rho=0.75$ \si{\ohm cm}\cite{Koffyberg1979}\\ 
10 $\mu$m powder layer & 2.6   &   PL at liquid nitrogen & \cite{Paracchini1982b}\\ 
amorphous film & 3.1 & photo-current &\cite{DiQuarto1981} \\
amorphous film & 2.7 & photo-current &\cite{Butler1976} \\
(001) surface of \ce{WO3} crystal &  & UV photoemission spectroscopy &\cite{Bringans1981} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{calculation results}

@@

Under O poor condition, formation energy of Vo is -0.02 eV, almost spontaneous. \ce{WO3} hole diffusion length 150 nm; etching hydrothermal grown wo3 flakes in weak acidic condition; Mott-Schottly plot, positive slope as expected for n type, carrier density as 5.92E20 \si{cm^{-3}} \cite{Li2014g},

a comprehensive process of \ce{WO3} NP for ECD. \cite{Wojcik2014}

2D \ce{WO3} flakes, electron Hall mobility 12 \si{cm^2V^{-1}s^{-1}}, high charge transport due to high relative permittivity suppressing the Coulomb charge effects. \cite{Zhuiykov2014} After \ce{H+} intercalation the band gap reduced to 2.5 eV. carrier mobility 275 \si{cm^2V^{-1}s^{-1}} for exfoliated Q2D \ce{WO3-x}, commercial Si-basded device about 500 \si{cm^2V^{-1}s^{-1}}. Ohmic contact between Q2D wo3-x and Au electrode,

\cite{Hutter2014}

### 2014-11-21 misc/paper.tex
misc works of paper reading, wo3 raman table etc
SI papers reading

\section{misc}

@@

@@

@@

@@

\textbf{junctions}
p-n homojunctions, p-n or n-n heterojunctions, metal-semi junctions, most important types: Schottky barriers, or ohmic contact.

chemical potential (Fermi level) as a measure of particle concentration.  Fermi level at 0K is equal to Fermi energy, which is defined as the energy of the topmost filled orbital. In equilibrium, the Fermi level $E_f$ is uniform throughout the material. n electron carrier, p holes carrier.

@@

@@

@@

>>>>

\section{misc: vls, crystal,}

@@

lateral growth, \cite{Zhang2014c}

@@

arixv: 1411.3774: current transport across metal-semi interface treated as thermionic emission:
\[
J(V_D) = J_S(\exp\frac{qV_D}{nkT}-1)
\]
where 
\[
J_S = \frac{4\pi q m^* k^2T^2}{h^3}\exp(-\frac{q\Phi_B}{kT})
\]

arix: 1411.2815: graphene on Cu.

The invention of efficient blue LEDs has led to white light sources for illumination. When exciting a phosphor material with a blue LED, light is emitted in the green and red spectral ranges, which, combined with the blue light, appears as white.

@@

by Kevin

@@

\textbf{junctions}
\begin{itemize}
\item p-n homojunctions,
\item p-n or n-n heterojunctions,
\item metal-semi junctions, 
\item metal-insulator-semi 
\end{itemize}

most important types: Schottky barriers, or ohmic contact.

chemical potential (Fermi level) as a measure of particle concentration.  Fermi level at 0K is equal to Fermi energy, which is defined as the energy of the topmost filled orbital. In equilibrium, the Fermi level $E_f$ is uniform throughout the material. n electron carrier, p holes carrier. concentration gradient,

@@

The built-in potential for a homojunction is equal to the full amount of band bending in equilibrium.

Gaussian surface and space charge neutral,

@@

A simple python script for this task can be found at \url{http://pythonhosted.org/eq_band_diagram/}.

\section{Semiconductor Statistics}

Band theory: broadening of the discrete quantized energy levels or the collective electron point of view. 
Drude's model:
\[
\kappa/\sigma = 3 (\frac{k}{e})^2T
\]

infinitesimal range $dp$, the absence of a ground state in orthohelium; for a system of indistinguishable particles which occupy quantum states in accordance with the Pauli principle, the thermal equilibrium probability of occupancy for a state of energy E is 
\[
f(E) = (1+\exp(\frac{E-\phi}{kT}))^(-1).
\]

Only for energies within a few $kT$ of $\phi$ is the probability of occupancy appreciably different from zero or unity. $\phi$ is determined by the condition that the number of occupied states at all energies must be equal to the total number of electrons present:
\[
n_0 = \int_{-\infty}^{\infty} f(E)g(E)dE
\]

At 0 K, Fermi level is given by 
\[
\phi_0 = \frac{h^2}{2m}(\frac{3n_0}{8\pi})^{2/3},
\]
whic is about 5 eV for monovalent metal. 200 times of $kT$ for RT. Only electrons near Fermi level contribute significantly to conductivities. separation of the concepts of free electron and conduction electron, where in the energy range $\partial f/\partial E$ is finite can be regarded as conduction electrons.

band theory based on a single electron approximation. crystal potential into Schrodinger Equation:
\[
\psi = U_k(r)\cdot\exp(ikr),
\]

In perfect crystal, $\psi$ with imaginary $k$ is discard, like the evanescent wave with decay, and the corresponding energy range is forbidden energy bands. For E with real $k$, plane wave solution exists forming permitted electron bands. The permitted wave function $\psi$ are the same in every unit cell of a periodic lattice, and the electron wave is not attenuated, i.e., an infinite mean free path emerging naturally in a perfect crystal. Scattering occurs due to defects, grain boundaries, imperfections developing localized energy states within the forbidden gaps, lattice vacancies, and the modulation of interatomic spacing be thermal vibration.

Brillouin zone drawing. Each BZ occupies the same volume of k-space, accommodating 2N electron states, where N is the total number of atoms in the crystal. Inner shell electrons are closely associated with a single nucleus; whereas the outermost electrons belong to the crystal as a whole.

electron can interchange states, with no observable result. electron and hole as real particles,

donor center moves or not?

multi-electron theories validate all the qualitative feature of simple band theory. How much does an electron deform the lattice in its vicinity? This is the question of the distinction between a free electron and a polaron.

One-electron band theory ignores multiplet structure: exciton, and orbital overlapping.

electrical properties of some metal and semiconductors are virtually unchanged in melting, suggesting a band structure is preserved even though there is no long range order. The dividision of permitted electron states into groups is dicated by the nature of short-range order, which hold in highly ordered crystal, in an amorphous phase or liquid phase of the same solid.

group velocities of an electron wave-packet in space is 
\[
v = \frac{\hbar}{\Delta_k E}
\]
, electron energy E(k) can be plotted as a multi-value function within the first BZ.

effective mass tensor has positive principal values at the lowest energy in a band, and negative ones at the top of a band. In both tight binding method and nearly free electron method, the E dispersion on wave-vector k can be written as 
\[
E = E_c + \frac{\hbar^2(k-k_c)^2}{2m_c}
\]
just above the bottom of a band; and 
\[
E = E_v - \frac{\hbar^2(k-k_v)^2}{2m_v}
\]
near the top of a band.

General expression of DOS is 
\[
g(E) =  \int \frac{dS}{4\pi^3\Delta_kE}
\]
and using effective mass renormalization, the wave-functions can be solved by
\[
\frac{\hbar^2}{2m^*} \Delta^2\psi + E\psi = 0
\]

Si conduction band minimum along [100] direction, about 25\% near the edge. Flaw encompasses foreign atoms, vacancies, interstitials.

When $n_0$ is large and $T$ is small, electron distribution is degenerate, all states are occupied up to an energy one or two kT short of the Fermi level; when $n_0$ is small and $T$ is not too low, occupied state lie within three or four kT above Ec, and Fermi level below Ec.

tabulation of Fermi-Dirac integral,

\[
n_0 = N_c F_{1/2}(\eta) = 2(2\pi mkT/h^2)^{3/2}F_{1/2}(\frac{\phi - E_c}{kT})
\]

For classical or non-degenerate semiconductor, the total number of electrons in CB is given by
\[
n_0 = N_c\exp(\frac{\phi - E_c}{kT})
\]
and $N_c$ acts as effective density of states. In analog, hole density can be written as

\[
p_0 = N_v\exp(\frac{-\phi - E_v}{kT})
\]

To evaluate the Fermi level dependency on $T$ at non-degenerate conditions, 
\[
\frac{d\phi}{d(kT)} \approx - (3/2 + \log(N_c/n_0))
\]

For intrinsic semiconductor, $n_0= p_0 = n_i$ set the position of Fermi level, which is the root of equation
\[
 N_c F_{1/2}(\eta) =  N_v F_{1/2}(-E_i - \eta)
\]
In non-degenerate limiting form, 
\[
\phi_i = E_c - 1/2E_i + 3/4kT\log(N_v/N_c)
\]
based on thermal equilibrium, where the same electrochemical potential should be experienced by all states.

degeneracy occurs when $E_c - \phi$ became negative.

For extrinsic situation, 
\[
\frac{n_0p_0}{n_i^2} \leq 1
\]

Define $N_r = n_0 - p_0$ as the difference between densities of impurity states, then in terms of $n_i$ and $N_r$, at low temperature when intrinsic excitation is feeble, 
\begin{align}
n_0 &\approx N_r + n_i^2/N_r\\
p_0 &\approx n_i^2/N_r
\end{align}

minimum energy and maximum entropy, electrical neutrality, iterative technique,

$N_d$ donor impurity atoms per unit volume, $N_di$ density of ionized donor atoms, wave function of s character,

Electron trapped in ground state and excited states, anisotropic elastic strain, attacked piecemeal,

extrinsic semiconductor is always partially compensated; $N_a$ total density of electron for acceptors. elementary manipulation leads to; rearranged to read as

a donor impurity is electrically neutral whether it has an electron bound in the ground state at Ec - Ed or in an excited state closer to the conduction band.

semilogarithmic plot, donor states impacted by excited states, split ground states, anisotropic strain,

amphoteric impurities, either donor or acceptor depending on F level, such as Au in germanium.

@@

\section{Transparent conductive oxides}

set the scene, ingredient, synthetic chemical routes, be of value, TCO, creep into, . \cite{Edwards2004}

$\sigma = ne\mu$, with $n$ as \si{cm^{-3}}, $e$ as C, and $\mu$ in \si{cm^2\per V\per s}. Then $\sigma$ in unit of \si{A\per V \per cm}.

A materials sorting map based on $n-\mu$. ITO with $\mu\sim10^4$ \si{\per\ohm cm^{-1}}. If the conductivity is sufficiently high, the thermal emittance is accordingly low. High $\sigma$ in ITO is related to the presence of shallow donor or impurity states ($\sim kT$) located close to the \ce{In2O3} CB, produced via \ce{Sn4+} doping for \ce{In3+} or oxygen vacancy. Thermal ionization promote the excess or donor electron into CB, giving rise to far-infrared absorption. At the same time, the host band gap is left intact.

nonmetal-to-metal transition, itinerant-electron scattering,

\ce{SnO2} into \ce{In2O3} as substitutional dopant, Sn with outer-shell electron configuration as $5s^25p^2$, and In as $5s^25p^1$. The Schrodinger wave solutions gives Bohr radius, $a_H \sim 13$ \si{\angstrom} for isolated ions, a large orbit extending many crystal cells, but localized at donor center?

\[
n^{1/3}\cdot a_H = \text{const.}
\]
or 
\[
k_Fl_e \approx 1
\]
where Fermi wavenumber $k_F = (3\pi^2n)^{1/3}$, $le$ is the mean free path.

The conductivity when $T\rightarrow 0K$ is used to discern metal from nonmetal, where the former always display finite conductivity, and the latter presumably extrapolated to zero.

optical window for ITO is set at short wavelength by direct band gap and at longer wavelength by its plasma edge, determined by the $n$.

In essence, the role of host matrix in (Metal-to-Nonmetal)MNM transition is important primarily in that it determines the form of the radial distribution of localized impurity state.\cite{Edwards1978}

\[
n_c^{1/3}\cdot a_H = K
\]

Isotropic Bohr radius is calculated from experimental ionization energy of localized state via $e^2/2\epsilon_{st} E_{expt}$.
The critical density $n_c$ for \ce{WO3:Na} is estimated to be $4\times 10^{22}$ \si{cm^{-3}}, with experimental value $a_H^* = 1.3$ \si{\angstrom}.

W as the unperturbed bandwidth of an array of one-electron state, and U as the intradonor Coulomb repulsion energy, which is the primary driving force in transition from metallic to insulating states.

\begin{align}
\psi(r) &= \sum_j \alpha_j F_j(r)\phi_j(r)\\
F(r) &= (\pi a_H^{*3})^{-1/2} \exp(-r/a_H^*)
\end{align}

An overlap-correlation problem,

delicate interpretation of experimental findings, strong dependency of RM m-\ce{WO_{3-x}} electronic properties on $V_O$ concentration and crystallographic direction along which $V_O$ is created.\cite{Wang2011b}

Coloration and electron conductivity changes. \citeauthor{Wang2011b} found strong dependence of WO3-x electronic properties on $V_O$ concentration and the the crystallographic direction on which O is removed. DFT band gap calculation is close to experimental value. Vacancy levels are found at 2.1 eV. When $V_O$ is in x axis, the associated electronic state is about 1 eV below CBM,

\section{ZnTe}

Zn rich suppress NW growth, Zeiss U55 SEM, XF3050 silicon drift detector, Quantax software from Bruker.EDX mapping show uniform Zn and Te distribution along NW, no atomic ratio is inferred. \cite{Rueda-Fonseca2014}

ZnTe, p type, band gap 2.25 eV. I_LO intensity ratio: area or height?

PL 1.88 eV, O impurity substituted isoelectronically. second order scattering, energy of scattered photons differs from the incident ones by two vibrational quanta.  \cite{Irwin1970}

photon occupation number, $n_j = (\exp(h\nu/kT) - 1)^{-1}$,

The coupling strength of the electron-phonon interaction can be evaluated by comparing the relative intensities of the overtones to the fundamental Raman band. DUring the steady-state Raman measurement, the trapped charge would build up producing a local electric field, which polarize the exciton. \cite{Zhang2012}

integrated intensities.
